Investigating Determinism of Game Engines for Autonomous Vehicle Verification

### 2020-04-15 paper/cav_determinisim_main.tex
still III.A

\subsection{Setting a Determinism  Threshold}
We use the term \textit{determinism threshold} to refer to the acceptable level of actor path variance ($\sigma^2$), which is quoted in terms of deviation ($\sigma$) for ease of interpretation. This threshold is analogous to the analogue signal level associated with each of the binary states of the signals in digital circuits. At some low analogue voltage the signal is interpreted as binary $0$, this may be below 0.5V, and the same signal is interpreted as binary $1$ at some higher voltage, e.g.\ above 3.5V.

The level of variance acceptable for the simulation must first be set. It serves as a threshold for deterministic execution. This level depends on the objectives of the simulation and the granularity at which the simulation environment operates. 
%
\todo{KIE HERE}
In our case study, presented in Section~\ref{s:case-study}, a threshold must be chosen for our given application which reflects the scale at which repeatability of simulation execution is required. This value must be sufficiently small to allow accurate \textit{assertion checking} of the ego vehicle in the environment but a larger value may be acceptable for non-urban environments, e.g. motorway or highway. Similarly, the threshold value should not be so small as to fail with minor computational bottlenecks, e.g. $1\mu m$. Two autonomous vehicle projects this group are involved in, Robopilot and Capri, are looking at urban mobility and last mile delivery solutions which are predominantly concerned with urban environments rather than highway or motorway scenarios. Because of this, a deterministic threshold of $1m$ is insufficient when considering potentially dangerous close passing of cyclists and pedestrians and therefore a threshold of $1cm$ is more suitable.

>>>>

\subsection{Setting a Determinism  Threshold}
The level of variance acceptable for a simulation must first be set. It serves as a threshold for deterministic execution.
%
We use the term \textit{determinism threshold} to refer to the acceptable level of actor path variance ($\sigma^2$), which is quoted in terms of deviation ($\sigma$) for ease of interpretation. 
%
This threshold is analogous to the analogue signal level associated with each of the binary states of the signals in digital circuits. At some low analogue voltage the signal is interpreted as binary $0$, this may be below 0.5V, and the same signal is interpreted as binary $1$ at some higher voltage, e.g.\ above 3.5V. This convention enables the abstraction from the physical signal values that are analogue voltages into the digital domain with binary representation.

The determinism threshold depends on the objectives of the simulation and the granularity at which the simulation environment operates. In particular, this threshold must be sufficiently small to enable accurate assertion checking. \todo[inline]{Make sure assertion checking has previously been introduced.}
%

\todo[inline]{KIE: Move this to the Case Study section.}
In our case study, presented in Section~\ref{s:case-study}, a threshold must be chosen for our given application which reflects the scale at which repeatability of simulation execution is required. This value must be sufficiently small to allow accurate \textit{assertion checking} of the ego vehicle in the environment but a larger value may be acceptable for non-urban environments, e.g. motorway or highway. Similarly, the threshold value should not be so small as to fail with minor computational bottlenecks, e.g. $1\mu m$. Two autonomous vehicle projects this group are involved in, Robopilot and Capri, are looking at urban mobility and last mile delivery solutions which are predominantly concerned with urban environments rather than highway or motorway scenarios. Because of this, a deterministic threshold of $1m$ is insufficient when considering potentially dangerous close passing of cyclists and pedestrians and therefore a threshold of $1cm$ is more suitable.
